---
title: "Linear Regression Project"
author: "Karthikeyan Ramachandran"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Get the data
```{r}
bike <- read.csv(file="data/bikeshare.csv", header=TRUE)
head(bike)
```

We're interested in predicting the `count` - Number of bike rentals

# Exploratory Data Analysis

```{r}
library(ggplot2)
ggplot(data=bike, aes(x=temp, y=count)) +
  geom_point(alpha=0.3, aes(col=count))
```

```{r}
attach(bike)
datetime.dt <- as.Date(datetime)

ggplot(data=bike, aes(x=datetime.dt, y=count)) +
  geom_point(aes(col=temp), alpha = 0.3) +
  scale_color_gradient(low = 'green', high = 'red')
```

The correlation between temperature and count is : `r cor(temp, count)`

```{r}
ggplot(data=bike, aes(x=factor(season), y=count)) +
  geom_boxplot(aes(col=factor(season))) +
  theme_bw()
```

```{r}
dt.posix <- as.POSIXct(datetime)
bike$hour <- format(dt.posix, "%H")
```

Bike rental count vs Hours on working days

```{r}
attach(bike)
ggplot(data.frame(filter(bike,workingday==1)), aes(x=hour, y=count)) +
  geom_point(position=position_jitter(w=1,h=0), aes(col=temp)) +
  scale_color_gradientn(colours = c('dark blue','blue','light blue','light green','yellow','orange','red')) +
  theme_bw()
```

Bike rental count vs Hours on non working days

```{r}
ggplot(data.frame(filter(bike,workingday==0)), aes(x=hour, y=count)) +
  geom_point(position=position_jitter(w=1,h=0), aes(col=temp)) +
  scale_color_gradientn(colours = c('dark blue','blue','light blue','light green','yellow','orange','red')) +
  theme_bw()
```

# Building the model

```{r}
temp.model <- lm(count~temp, data=bike)
summary(temp.model)
```

## Model summary:
* The F-statistic is greater than 1, which suggests that the predictors have significant relationship with the response
* The temp has an estimated coefficient of 9.1705, so for every unit increase of temp the bike rental count increases by 9.17 units.

```{r}
predict(temp.model, newdata=data.frame(temp=25))
```

```{r}
bike$hour <- as.numeric(bike$hour)
```

```{r}
lm.fit <- lm(count~season+workingday+weather+temp, data=bike)
summary(lm.fit)
```

